MJSLAAM: Designing a Sound, Configurable, Efficient, and Pushdown Monadic Static~Analyzer for JavaScript

### 2014-12-13 cs252r-fa14-writeup/paper.tex
ready to send to Steve

\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amssymb}

@@

\begin{itemize}
\item Design a configurable static analysis for javascript using the
  Monadic Abstracting Abstract Machines (\maam{}) \cite{maam} design process.
\item Implement the analysis using the \maam{} framework as implemented in Haskell.
\item Analyze the performance of many different analysis techniques, including
  pushdown analysis, against the JSAI \cite{jsai} benchmark suite.
\end{itemize}

We completed the first goal, part of the second, and none of the third.
%
We underestimated the time necessary to implement the semantics of \js{} in the
\maam{} Haskell framework.
%
We were unable to complete a full implementation of the \js{} spec and
therefore unable to run our interpreter on the full JSAI~\cite{jsai} benchmark
suite.
%
However, we were successful in running our analysis on small programs which
reside in the subset of \js{} that we were able to implement.
%
We also spent a significant amount of time understanding pushdown analysis and
recasting it in the \aam{} and \maam frameworks.

@@

Step 3. yields a larger machine, C-E-S-KS-K*-\$ machine, which adds a new component:
\begin{equation*}
\$ : C \times E \times S \rightarrow Val + \{SEEN\} + \{UNSEEN\}
\end{equation*}
%
The fact that the cache can memoize invariant to the continuation is
traditionally understoon in the pushdown literature as by-product of viewing
the semantics a pushdown automata.
%
We propose another intuition: the CEK machine comes from a \emph{reduction}
semantics--a setting where reduction is defined invariant to context to begin
with.

@@

\begin{lstlisting}
data Frame =
    LetK [(Name, Set AValue)] Name [(Name, TExp)] TExp
  | AppL [TExp]
  | AppR (Set AValue) [(Set AValue)] [TExp]
  | ObjK [(String, (Set AValue))] Name [(Name, TExp)]
    -- Array Dereferencing
  | FieldRefL TExp
  | FieldRefR (Set AValue)
    -- Array Assignment
  | FieldSetA TExp         TExp
  | FieldSetN (Set AValue) TExp
  | FieldSetV (Set AValue) (Set AValue)
    -- Property Deletion
  | DeleteL TExp
  | DeleteR (Set AValue)
    -- Fig 2. Mutable References
  | RefSetL TExp
  | RefSetR (Set AValue)
  | RefK
  | DeRefK
    -- Fig 8. Control Operators
  | IfK TExp TExp
  | SeqK TExp
  | WhileL TExp TExp
  | WhileR TExp TExp
  | LabelK Label
  | BreakK Label
  | TryCatchK TExp Name
  | TryFinallyL TExp
  | TryFinallyR (Set AValue)
  | ThrowK
    -- Fig 9. Primitive Operations
  | PrimOpK Op [(Set AValue)] [TExp]
  deriving (Eq, Ord)
instance PartialOrder Frame where pcompare = discreteOrder
\end{lstlisting}
\caption{The Frame, i.e., Continuation Datatype}
\end{figure}

\begin{lstlisting}
pushFrame :: (Analysis $\varsigma$ m) => Frame -> m ()
pushFrame fr = do
  fp  <- getL konL
  fp' <- nextFramePtr
  modifyL kstoreL (mapInsertWith (\/) fp' (singleton (fr, fp))
  putL konL fp'

@@

The third item is the main contribution of this project.

@@

The \maam{} framework separates the semantics of a programming language from the
control flow. This same implementation of \lambdajs{} can be used with different
monads to produce path and flow sensitive analysis, as well as other kinds of
analysis. With an appropriate set of monads, traditional points-to constraints
could be generated. We note that we did not in the end implement each of these
analyses for \js{}, although we plan to do so in our continuation of this work.

@@

@@

>>>>

\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{hyperref}

@@

\begin{itemize}
  \item Design a configurable static analysis for \js{} using the
  Monadic Abstracting Abstract Machines (\maam{}) \cite{maam} design process.
\item Implement the analysis using the \maam{} framework as implemented in Haskell.
\item Analyze the performance of many different analysis techniques, including
  pushdown analysis, against the JSAI \cite{jsai} benchmark suite.
\end{itemize}

We completed the first goal, part of the second, and none of the third.
%
We underestimated the time necessary to implement the semantics of \js{} in the
\maam{} Haskell framework.
%
We were unable to complete a full implementation of the \js{} spec and
therefore unable to run our interpreter on the full JSAI~\cite{jsai} benchmark
suite.
%
However, we were successful in running our analysis on small programs which
reside in the subset of \js{} that we were able to implement.
%
We also spent a significant amount of time understanding pushdown analysis and
recasting it in the \aam{} and \maam{} frameworks.
%
Finally, we plan on continuing this work during the coming weeks to realize the
full potential of our efforts, with the aim of accomplishing all three project
goals.

@@

Step 3. yields a larger machine, C-E-S-KS-K*-\$ machine, which adds a new component:
\begin{equation*}
\$ : C \times E \times S \rightarrow Val + \{SEEN\} + \{UNSEEN\}
\end{equation*}
%
The fact that the cache can memoize invariant to the continuation is
traditionally understood in the pushdown literature as by-product of viewing
the semantics a pushdown automata.
%
We propose another intuition: the CEK machine comes from a \emph{reduction}
semantics--a setting where reduction is defined invariant to context to begin
with.

@@

% \begin{figure}
% \centering
% 
% \begin{lstlisting}
% data Frame =
%     LetK [(Name, Set AValue)] Name [(Name, TExp)] TExp
%   | AppL [TExp]
%   | AppR (Set AValue) [(Set AValue)] [TExp]
%   | ObjK [(String, (Set AValue))] Name [(Name, TExp)]
%     -- Array Dereferencing
%   | FieldRefL TExp
%   | FieldRefR (Set AValue)
%     -- Array Assignment
%   | FieldSetA TExp         TExp
%   | FieldSetN (Set AValue) TExp
%   | FieldSetV (Set AValue) (Set AValue)
%     -- Property Deletion
%   | DeleteL TExp
%   | DeleteR (Set AValue)
%     -- Fig 2. Mutable References
%   | RefSetL TExp
%   | RefSetR (Set AValue)
%   | RefK
%   | DeRefK
%     -- Fig 8. Control Operators
%   | IfK TExp TExp
%   | SeqK TExp
%   | WhileL TExp TExp
%   | WhileR TExp TExp
%   | LabelK Label
%   | BreakK Label
%   | TryCatchK TExp Name
%   | TryFinallyL TExp
%   | TryFinallyR (Set AValue)
%   | ThrowK
%     -- Fig 9. Primitive Operations
%   | PrimOpK Op [(Set AValue)] [TExp]
%   deriving (Eq, Ord)
% instance PartialOrder Frame where pcompare = discreteOrder
% \end{lstlisting}
% \caption{The Frame, i.e., Continuation Datatype}
% \end{figure}

@@

The third item is the main contribution of this project.
The architecture of our executable analysis is shown in Figure 2.

@@

The \maam{} framework separates the semantics of a programming language from the
control flow. This same implementation of \lambdajs{} can be used with different
monads to produce path and flow sensitive analysis, as well as other kinds of
analysis. With an appropriate set of monads, traditional points-to constraints
could be generated. We note that we did not in the end implement each of these
analyses for \js{}, although we plan to do so in our continuation of this work.
Our implementation is accessible at \url{https://github.com/davdar/maam}
under the path "src/Lang/JS/".

@@

We show two code snippets from our implementation in Figure 3.
[pushFrame] shows the monadic action for pushing a continuation frame, which
consists of: getting the current continuation pointer; getting the 
continuation pointer to allocate; and adding a new continuation frame to the
continuation store.
[popFrame] shows the monadic action for popping continuation frames. The popped
frame will scrutenized to determine the  control state of the program, and
as a result, the set of frames returned from the continuation store must be
merged into the monad. This merging is done with the [mset] operator 
$(mset : \forall(a). \mathcal{P}(a) \rightarrow m(a))$.

@@

\begin{lstlisting}
pushFrame :: (Analysis $\varsigma$ m) => Frame -> m ()
pushFrame fr = do
  fp  <- getL konL
  fp' <- FramePtr
  modifyL kstoreL (mapInsertWith (\/) fp' (singleton (fr, fp))
  putL konL fp'
